This document serves as a comprehensive guide to the functional and non-functional requirements of the \textbf{iBrief} application. It provides a detailed overview of the key features, behaviors, and interfaces to be implemented in its inaugural release.

\subsection{Objective}
    The primary objective of this document is to offer a structured and lucid insight into the \textbf{iBrief} application's requirements. Specifically, it aims to:
        \begin{itemize}
            \item Define the core functionalities, behaviors, and expectations of the application.
            \item Establish a consistent foundation for development, design, and testing activities.
            \item Serve as an authoritative reference for all project stakeholders, ensuring alignment in understanding and expectations.
            \item Detail the user interface (\gls{UI}) design and workflow for the \gls{mobile application}s.
            \item Guarantee alignment with overarching project objectives and user requirements.
        \end{itemize}

\subsection{Scope}
    This document encompasses both the functional and non-functional aspects of the \textbf{iBrief} application. It emphasizes the features and behaviors that are central to its primary functionality and provides a road-map for its development trajectory, covering the initial release and setting the stage for subsequent enhancements.

    By meticulously documenting the functional requirements, non-functional constraints, and \gls{UI} expectations, this document ensures a shared understanding of the \textbf{iBrief} application's mission and capabilities among all project participants. It remains a crucial touchstone throughout the development life-cycle, aiding in the successful realization and launch of the \textbf{iBrief} application.





