\subsection{Terminology}
Throughout this requirement document, specific terminology and conventions are utilized to ensure clarity and emphasis:
    \begin{itemize}
        \item \textbf{Term in Bold:} Important project-related terms, concepts, or headings, such as "\textbf{iBrief}" or "\textbf{Product Scope}," are highlighted using bold.
        
        \item \textit{Italicized Term:} Italics emphasize specific terms, or indicate variables or placeholders, like \textit{user stories} or \textit{deliverable}.
        
        \item \texttt{Monospaced Text:} Technical elements, including \texttt{code snippets} or \texttt{file paths}, are represented using a monospaced font.
        
        \item \text{[Square Brackets]}: Square brackets indicate placeholders, e.g., [Project Sponsor's Name] or [Date], to be replaced with contextually relevant information.
    \end{itemize}

\subsection{Abbreviations and Acronyms}
For conciseness and clarity, this document incorporates abbreviations and acronyms. A comprehensive list of these can be found in appendix \ref{apn:glossary}.

\subsection{Formatting Conventions}
This document adheres to the following formatting conventions for consistency and enhanced readability:

    \begin{itemize}
        \item \textbf{Section Headings:} Headings are numbered and presented in title case, facilitating quick navigation and reference.
        
        \item \textit{Italicized Text:} Italics are reserved for emphasis, variable names, and placeholders.
        
        \item \texttt{Monospaced Font:} Code snippets, \gls{URL}s, file paths, and other technical references employ a monospaced font.
        
        \item Bullet Points and Enumerations: Lists use bullet points, while sequential or numbered lists employ enumerations.
        
        \item \textbf{Hyperlinks:} External resources or web addresses are represented as hyperlinks, typically colored and underlined.
    \end{itemize}

\subsection{References and Citations}
All external references, be it to documents, standards, or other resources, are cited in alignment with recognized citation styles like IEEE, APA, or a designated company standard.

\subsection{Version Control}
Version control is in place for this document, ensuring accurate tracking of changes and revisions. The document's revision history provides a detailed record of edits over time.

\subsection{Review and Approval}
Key stakeholders, including the project sponsor and project manager, review and approve this requirements document. This process guarantees alignment with the overarching project vision and objectives.
