\subsection{Intended Audience}
This requirements document is crafted for a diverse set of stakeholders, both technical and non-technical. The intended audiences include:

    \begin{itemize}
        \item \textbf{Development Team:} Software developers and programmers tasked with realizing the application's functionalities based on the specifications provided.
        
        \item \textbf{Design Team:} \gls{UI} and \gls{UX} designers shaping the visual layout and ensuring optimal user interaction with the application.
        
        \item \textbf{Testing Team:} \gls{QA} professionals validating the application's conformity to its functional requirements and ensuring robustness.
        
        \item \textbf{Project Management:} Overseeing the project's progression, timelines, and resource allocation.
        
        \item \textbf{Stakeholders:} Including project sponsors, investors, system architects, local authorities, government agencies, and \gls{end-user}s such as citizens.
        
        \item \textbf{Documentation Team:} Drafting user manuals, help guides, and other relevant documentation using this document as a primary reference.
    \end{itemize}

This document offers insights tailored to each audience. Technical teams will find detailed specifications, while non-technical stakeholders can grasp the overarching project vision and objectives.

\subsection{Reading Suggestions}
For a structured navigation through this document, we suggest the following approach:

    \begin{itemize}
        \item \textbf{Project Overview:} Begin with the "Project Description" for a holistic understanding of the \textbf{iBrief} application's vision.
        
        \item \textbf{Product Scope:} Delve deeper into the "Product Scope" for insights on the application's functionalities, objectives, and key deliverables.
        
        \item \textbf{Stakeholder Perspective:} The "Stakeholders" section elucidates the primary entities associated with the project and their roles.
        
        \item \textbf{Technical Details:} Technical members should explore the technical specifics in the "Product Scope" and other relevant sections.
        
        \item \textbf{Dependencies and Risks:} The "Dependencies" and "Risks" sections shed light on potential challenges and interdependencies.
        
        \item \textbf{Change Control and Approval:} Familiarize yourself with the modus operandi for managing project changes in the "Change Control" section, wrapping up with the "Approval" section.
        
        \item \textbf{Appendices and Additional Resources:} Supplement your understanding by referring to appendices and any provided additional resources.
    \end{itemize}
    
Active engagement, discussions, and seeking clarifications are encouraged to ensure all stakeholders share a unified understanding of the project's scope and aspirations.
