The safety of users and the integrity of the data they provide are of paramount importance for the \textbf{iBrief} application. Given the application's role in issue reporting and its integration capabilities, it is vital to ensure that data is handled securely, user privacy is maintained, and the system is protected against potential threats. The following are the key safety requirements:

\begin{itemize}
    \item \textbf{Data Protection and Encryption}: All user data, including personal information, reported issues, and media attachments, should be encrypted both in transit and at rest. This ensures that sensitive information remains confidential and is protected against unauthorized access or breaches.
    
    \item \textbf{Authentication and Authorization}: The application should implement robust authentication mechanisms, such as multi-factor authentication, to ensure that only authorized users can access the system. Role-based access controls should also be in place to ensure users can only access features and data pertinent to their roles.
    
    \item \textbf{Anti-fraud Measures}: Implement AI-driven mechanisms to detect and prevent fake issue reporting by identifying patterns of false reports or suspicious user behavior.
    
    \item \textbf{Content Safety}: Implement filters and checks to prevent the upload of malicious content, offensive language, or inappropriate media. Automatic content scanning tools can be used to flag or block potentially harmful content.
    
    \item \textbf{Backup and Recovery}: Regular backups of the application's data should be scheduled to ensure that, in case of any system malfunctions or failures, data can be recovered without significant loss.
    
    \item \textbf{Audit Trails}: Maintain detailed logs of all user actions and system activities. This ensures that any malicious or unauthorized activities can be traced back to their source, aiding in investigations and accountability.
    
    \item \textbf{Regular Security Audits}: Periodically conduct security audits and vulnerability assessments to identify and address potential weaknesses in the system. This proactive approach ensures the application remains resilient against evolving security threats.
    
    \item \textbf{Data Retention and Deletion}: Define clear policies for data retention, ensuring data is not kept longer than necessary. Users should also have the capability to delete their accounts and associated data, adhering to data privacy regulations.
\end{itemize}

By adhering to these safety requirements, the \textbf{iBrief} application will not only offer a secure environment for its users but will also earn their trust by ensuring the protection of their data and fostering a safe platform for community interactions.

