The \textbf{iBrief} application is designed not only to meet functional requirements but also to excel in software quality attributes that ensure a robust, reliable, and user-friendly system. The following are the key quality attributes that the application emphasizes:

\begin{itemize}
    \item \textbf{Reliability:} The \textbf{iBrief} application is designed to operate consistently and accurately, minimizing system failures and ensuring that reported issues are managed and resolved appropriately.

    \item \textbf{Usability:} With an intuitive user interface and clear navigation paths, the application is user-friendly, catering to both tech-savvy individuals and those less familiar with digital tools.

    \item \textbf{Maintainability:} The system's modular design allows for easy updates, bug fixes, and enhancements without affecting other parts of the application.

    \item \textbf{Scalability:} \textbf{iBrief} can accommodate a growing number of users and data entries without compromising on performance, ensuring that it remains efficient as user engagement increases.

    \item \textbf{Portability:} Developed to be compatible with major mobile platforms like \gls{iOS} and \gls{Android}, the application can be easily ported and adapted to various devices.

    \item \textbf{Performance:} The application is optimized to ensure quick response times, efficient resource utilization, and smooth user interactions, even during peak usage times.

    \item \textbf{Security:} Protecting user data and ensuring secure interactions are paramount. The application employs strong encryption, authentication mechanisms, and regular security audits to safeguard against potential threats.

    \item \textbf{Interoperability:} \textbf{iBrief} is designed to work seamlessly with various external systems and services, ensuring smooth data exchange and integration.

\end{itemize}

These software quality attributes play a pivotal role in making the \textbf{iBrief} application a reliable, efficient, and preferred choice for users and local authorities alike.

