Ensuring the continuous availability of the \textbf{iBrief} application is crucial for user trust, efficient issue management, and seamless interactions between all stakeholders. The application should be operational and accessible to users, authorities, and agents most of the time, minimizing any potential downtime. The following details the up-time and availability requirements:

\begin{itemize}
    \item \textbf{Up-time Target:} 
    The \textbf{iBrief} application should aim for a 99.9\% up-time annually. This corresponds to a maximum of 8.76 hours of unplanned downtime per year.

    \item \textbf{Scheduled Maintenance:} 
    Any scheduled maintenance activities, updates, or patches that may result in downtime should:
    \begin{itemize}
        \item Be communicated to users, authorities, and agents in advance.
        \item Be performed during off-peak hours or periods of low activity to minimize disruption.
        \item Include clear start and end times so that users can plan their activities accordingly.
    \end{itemize}
    
    \item \textbf{Disaster Recovery:}
    In the event of a significant disruption or system failure, there should be a disaster recovery plan in place that details:
    \begin{itemize}
        \item Rapid system restoration procedures.
        \item Data backup and retrieval protocols to prevent data loss.
        \item Communication channels to inform stakeholders about the issue and expected recovery times.
    \end{itemize}
    
    \item \textbf{Load Balancing and Scalability:}
    The system should employ \gls{load balancing} techniques to distribute incoming traffic and requests, ensuring optimal performance and responsiveness. Additionally, it should be scalable to handle spikes in user activity or increased issue reports without compromising availability.
    
    \item \textbf{Monitoring and Alerts:}
    Continuous monitoring tools should be in place to detect any anomalies or potential threats to system availability. Any detected issues should trigger automatic alerts to the technical team for swift action.

    \item \textbf{Backup Systems:}
    Regular backups of the application data, user accounts, and issue reports should be performed. These backups ensure data integrity and facilitate swift recovery in case of system failures or data corruption.

\end{itemize}

Upholding these availability and up-time requirements ensures that the \textbf{iBrief} application remains a reliable platform for its users, enhancing trust and ensuring efficient operations.
