The \textbf{iBrief} application operates based on a set of business rules that guide its functionalities and ensure consistency, integrity, and conformity to the organizational goals. These rules are intrinsic to the system's design and play a crucial role in managing user interactions, data processing, and system behaviors. The following are the primary business rules requirements:

\begin{itemize}
    \item \textbf{User Registration and Authentication:} 
    \begin{itemize}
        \item Only unique email addresses are allowed for user registration.
        \item Passwords must meet a specific complexity criterion, including length, alphanumeric characters, and special symbols.
        \item Users must verify their email addresses before they can report issues.
    \end{itemize}
    
    \item \textbf{Issue Reporting:} 
    \begin{itemize}
        \item Users can report issues only within predefined categories. 
        \item Each reported issue must have a location (either manual entry or GPS-tagged).
        \item Users cannot report more than a set number of issues within a 24-hour period to prevent spamming.
    \end{itemize}
    
    \item \textbf{AI Pre-processing:}
    \begin{itemize}
        \item Offensive words or phrases detected by the AI will be automatically redacted or flagged for review.
        \item Reports from users consistently flagged for misinformation may be deprioritized or subjected to additional verification.
    \end{itemize}

    \item \textbf{Dashboard for Authorities and Sales Team:}
    \begin{itemize}
        \item Only authorized personnel can access the dashboards.
        \item Changes made to issue statuses or user accounts must be logged and timestamped.
    \end{itemize}

    \item \textbf{Integration and Data Exchange:}
    \begin{itemize}
        \item Data exports (e.g., analytics, issue data) must be in standard formats (e.g., CSV, JSON).
        \item Any data imports or exchanges with third-party systems must undergo validation checks to ensure data integrity.
    \end{itemize}

    \item \textbf{Notifications:}
    \begin{itemize}
        \item Users should receive notifications only for issues they reported or subscribed to.
        \item Push notifications should not be sent more than a set frequency to prevent user annoyance.
    \end{itemize}

    \item \textbf{Data Retention and Privacy:}
    \begin{itemize}
        \item User data should be retained only for a specified period after which it should be anonymized or deleted.
        \item Users have the right to request the deletion of their accounts and associated data.
    \end{itemize}

\end{itemize}

Adherence to these business rules ensures that the \textbf{iBrief} application operates transparently, efficiently, and aligns with the organizational vision and user expectations.
