The \textit{Issue Management} module in the \textbf{iBrief} application is central to efficiently addressing urban challenges. This module enables both citizens and local authorities to collaboratively address and resolve city-based issues. Its functionalities encompass:

\begin{itemize}
    \item \textbf{Efficient Issue Reporting:}
    Users can swiftly report issues by adding detailed descriptions, attaching multimedia evidence, and pinpointing the precise location using integrated GPS functionality.
    
    \item \textbf{Real-time Issue Tracking:}
    Users can monitor the progression of their reports through real-time status updates, from initial submission to final resolution.
    
    \item \textbf{Issue Categorization:}
    Reports are systematically classified based on their nature, which aids in prioritizing and directing them to the relevant departments or authorities.
    
    \item \textbf{Issue Assignment:}
    Administrators or officers can assign particular issues to specific agents or teams, ensuring that the right personnel address the concern.
    
    \item \textbf{Collaborative Resolution:}
    Multiple stakeholders can collaborate on a single issue, share insights, add comments, and jointly work towards a solution.
    
    \item \textbf{Historical Data Analysis:}
    The system retains a history of all resolved and unresolved issues, enabling data-driven decision-making and trend analysis for future urban planning.
\end{itemize}

This comprehensive \textit{Issue Management} module ensures that urban concerns are not only identified but also effectively addressed, contributing to a more responsive and improved city environment.

