The \textit{Extended Dashboard for Sales Team} is a specialized feature within the "iBrief" application designed to empower sales team members with enhanced capabilities for managing customer relationships and account administration. This dedicated dashboard provides a range of features and tools to streamline sales operations and customer interactions.
    \begin{itemize}
        \item \textbf{Administrator Account Creation:}
        Sales team members have the authority to create administrator accounts for customers. These accounts grant customers administrative control over their accounts, enhancing their autonomy and management capabilities.
        
        \item \textbf{Account Management:}
        The dashboard facilitates the management of customer accounts by allowing sales team members to perform actions such as updating account information, extending subscription periods, and suspending accounts when necessary.
    
        \item \textbf{Customer List Management:}
        Sales team members have access to a comprehensive list of customers, allowing them to view, search, and manage customer records efficiently. This feature simplifies the process of identifying and addressing customer needs.
        
        \item \textbf{Contact Information Access:}
        The dashboard provides access to customer contact information, enabling sales team members to communicate with customers effectively. This includes email addresses, phone numbers, and other relevant contact details.
        
        \item \textbf{Issue Resolution and Support:}
        Sales team members can provide support to their direct customers and address any issues or concerns they may have. This feature fosters a proactive approach to customer service and relationship management.

        \item \textbf{Sales Forecasting:}
        Leveraging machine learning, the dashboard can predict sales trends, helping the team prepare for future opportunities or challenges.
    
        \item \textbf{Collaborative Tools:}
        Sales team members can collaborate on deals, share notes, and discuss strategies right within the dashboard, promoting teamwork and shared knowledge.
    \end{itemize}
    
The \textit{Extended Dashboard for Sales Team} empowers sales team members with the tools and capabilities needed to enhance customer relationships, streamline administrative tasks, and provide comprehensive support to customers. It plays a vital role in ensuring a seamless customer experience within the "iBrief" application.