The \textit{Extended Dashboard for Support Team} in the \textbf{iBrief} application serves as a pivotal tool tailored specifically for the support team. This feature-rich dashboard is meticulously designed to bolster the efficiency and effectiveness of the support team in assisting users and resolving issues.

\begin{itemize}
    \item \textbf{Specialized User Role:}
    This unique role is crafted to provide the support team with specialized tools and functionalities, enhancing their capability to assist users and manage issues.
    
    \item \textbf{User Authentication Assistance:}
    The dashboard facilitates a multi-layered verification system, which includes voice recognition and biometric verification, in addition to the conventional security questions.
    
    \item \textbf{Access to Specific Reports:}
    Enables the support team to delve deep into issue reports, offering advanced search filters, tags, and sorting options for better navigation and issue understanding.
    
    \item \textbf{Log Review for Issue Changes:}
    An enriched logging system that not only tracks changes but also allows annotations, ensuring that any crucial observations are not lost.
    
    \item \textbf{CRUD Functionality:}
    Apart from the standard CRUD operations, this functionality provides audit trails, ensuring that any changes made to data can be tracked back to the responsible individual.
    
    \item \textbf{Automatic Report Generation:}
    Advanced reporting tools that allow for custom report templates, scheduled report generation, and automated delivery to designated recipients.
    
    \item \textbf{User Feedback Collection:}
    Integrated tools for collecting, categorizing, and analyzing user feedback, ensuring that the voice of the user is always heard and acted upon.
    
    \item \textbf{Training Modules:}
    Embedded training modules and tutorials to keep the support team updated with the latest application features and best practices.
    
    \item \textbf{Performance Analytics:}
    Tools that provide insights into the performance of the support team, such as response times, resolution rates, and user satisfaction scores, helping in continuous improvement.
\end{itemize}

The \textit{Extended Dashboard for Support Team} not only augments the capabilities of the support team but also ensures that they have
