The \textit{User Account Management} module in the \textbf{iBrief} application serves as a secure gateway and personalized hub for all users. It offers:

\begin{itemize}
    \item \textbf{User Registration and Authentication:}
    Facilitates a streamlined registration process, complemented by robust authentication methods, to ensure users' data confidentiality and security.
    
    \item \textbf{Profile Management:}
    Allows users to update personal information, change profile pictures, and fine-tune preferences to enhance their application experience.
    
    \item \textbf{Password Reset and Recovery:}
    Provides features for users to reset forgotten passwords securely and enable multi-factor authentication for added security.
    
    \item \textbf{Notification Preferences:}
    Users can customize notification settings, deciding which updates they wish to receive and how (e.g., email, push notifications).

    \item \textbf{Look and Feel Preferences:}
    Users have the option to personalize the application's appearance according to their tastes. This includes choosing from predefined themes (e.g., light, dark, high contrast) and adjusting font sizes for improved readability. These customization options aim to enhance user experience and accessibility, catering to individual visual preferences and needs.
    
    \item \textbf{Account Deactivation and Deletion:}
    In line with data privacy regulations, users can choose to temporarily deactivate or permanently delete their accounts.
    
    \item \textbf{User Data Export:}
    Empowers users by allowing them to download and export their data, ensuring transparency and data portability.
\end{itemize}

This module emphasizes user-centric design, ensuring each user has full control over their account and data, fostering trust and confidence in the system.

