The \textbf{iBrief} application offers a robust, web-based dashboard designed to empower local authorities and administrators with a comprehensive toolset for efficient issue management. It provides a centralized platform for monitoring, communicating, and resolving reported city issues. Here are the key functionalities:

\begin{itemize}
    \item \textbf{Comprehensive Dashboard:}
    Local authorities and administrators access a holistic web-based dashboard, visualizing reported issues, their status, and associated metrics.
    
    \item \textbf{Geospatial Issue Mapping:}
    Issues are plotted on an interactive map, allowing authorities to identify problem hotspots and prioritize accordingly.
    
    \item \textbf{Data Analytics and Reporting:}
    The dashboard offers analytical tools and report generation capabilities for insights into issue patterns, resolution times, user feedback, and agent performance facilitating data-driven decision-making.
    
    \item \textbf{Task Assignment and Monitoring:}
    Issues can be delegated to specific agents or teams. Progress is tracked in real-time, with communication tools facilitating intra-agency coordination.
    
    \item \textbf{Feedback and Comment Management:}
    Authorities can review and respond to user comments, ensuring a two-way communication channel with the public.
    
    \item \textbf{Customizable Workflow:}
    The issue resolution process can be tailored by administrators to mirror the internal operations and preferences of each authority.
    
    \item \textbf{User and Role Management:}
    Administrators have the capability to add, modify, or remove users and define their roles, ensuring the right personnel have appropriate access levels.
    
    \item \textbf{Alerts and Notifications:}
    System-generated alerts notify authorities of critical issues, ensuring prompt attention to high-priority matters.
\end{itemize}

This advanced dashboard serves as a command center, equipping authorities with the necessary tools to address urban challenges proactively. It fosters a collaborative environment for effective city management, ultimately enhancing public services and citizen satisfaction.