User documentation for the \textbf{iBrief} application will be comprehensive and tailored to cater to various user classes and levels of expertise:

\begin{enumerate}
    \item \textbf{User Manuals:} A step-by-step guide providing a thorough walk-through of the application, including installation, setup, main features, and troubleshooting common issues.
    
    \item \textbf{Quick Start Guides:} A concise guide for users to quickly get started with the core functionalities of the application.
    
    \item \textbf{Video Tutorials:} Visual demonstrations on how to use the application effectively.
    
    \item \textbf{FAQ Section:} Addresses common queries and challenges that users might face.
    
    \item \textbf{Glossary:} A section defining technical terms, abbreviations, and acronyms.
    
    \item \textbf{Interactive Help:} An in-app feature where users can search for specific instructions or ask questions.
    
    \item \textbf{Feedback Mechanism:} A section in the documentation where users can provide feedback.
    
    \item \textbf{Version History and Update Notes:} Details about the application's various versions.

    \item \textbf{Safety and Privacy Guide:} A dedicated section on data handling and privacy policies.
    
    \item \textbf{Contact Details:} Providing users with contact information for further assistance.
    
    \item \textbf{Community Forums:} An online platform for user discussions.
    
    \item \textbf{Accessibility Guide:} Detailed guidelines designed to cater to users with various abilities. This includes provisions for visually impaired individuals, offering high-contrast views, and screen reader compatibility. The guide will also provide instructions on how to adjust application settings for an optimized and inclusive user experience.
\end{enumerate}

By offering a diverse range of user documentation resources, the \textbf{iBrief} application ensures that users have the necessary tools and knowledge at their disposal to maximize the app's utility.

