The \textbf{iBrief} application is designed to function seamlessly across a diverse range of environments, ensuring accessibility and efficiency for its users:

\begin{itemize}
    \item \textbf{Platform Compatibility:} Primarily a \gls{web-based} solution, the application is also optimized for mobile environments. It offers dedicated mobile applications for both \gls{iOS} and \gls{Android} operating systems, ensuring a broad reach and compatibility with a majority of modern smartphones and tablets.

    \item \textbf{Browser Support:} The application is compatible with all modern web browsers, including Google Chrome, Mozilla Firefox, Safari, and Microsoft Edge. Regular updates ensure that the application remains aligned with the latest browser versions and technologies.

    \item \textbf{Connectivity:} While an active internet connection is required for real-time issue reporting and tracking, the application is designed with offline capabilities. Users can report issues even without internet access; these reports are stored locally on the user's device. As soon as the device regains connectivity, these offline-stored issues are automatically submitted to the server, ensuring no data loss or reporting delays.

    \item \textbf{Location Services:} The application integrates with external location services to provide GPS-based issue tagging. For accurate and efficient reporting, users need to enable GPS functionality on their devices. The application ensures user privacy by seeking permission before accessing location data and only using it for the specified purpose of issue tagging.

    \item \textbf{Back-end Infrastructure:} The \gls{back-end} system, responsible for data storage, management, and processing, is hosted on a secure cloud infrastructure, ensuring \gls{scalability}, reliability, and robust data protection measures.

    \item \textbf{Integration Capabilities:} Recognizing the diverse IT landscapes of different cities, the \textbf{iBrief} application is designed with flexible integration capabilities. It can connect with various local authority systems, databases, and other relevant platforms, facilitating seamless data exchange and efficient issue resolution.
\end{itemize}

The robust and flexible operating environment of the \textbf{iBrief} application ensures that users experience a seamless, efficient, and intuitive interface, regardless of their device or location.
