The \textbf{iBrief} application is meticulously crafted to offer intuitive and user-friendly user interfaces (\gls{UI}) tailored for both iOS and Android platforms. The user interfaces incorporate the following elements:
    
    \begin{itemize}
        \item \textbf{Issue Reporting Interface:} Dedicated to enabling end-users to report issues effortlessly, it supports text descriptions, media attachments, and GPS-based location tagging.
        
        \item \textbf{Issue Tracking Interface:} Provides users with a real-time overview of their reported issues, ensuring they remain informed of any developments.
        
        \item \textbf{User Account Management:} Centralizes user-related functionalities such as registration, login, and settings modification.
        
        \item \textbf{Dashboard Interface:} A web-based platform that allows local authorities and administrators to have a holistic view of reported issues and manage them effectively.
        
        \item \textbf{Notification Interface:} Facilitates instant communication with users by delivering push notifications regarding issue updates, fostering user engagement.
    \end{itemize}

\subsection{Issue Reporting Interface}
    Specially designed to facilitate seamless issue reporting, this interface comprises:
    
    \begin{itemize}
        \item \textbf{New Issue Reporting:} A primary screen dedicated to reporting new issues.
        \item \textbf{Issue Description and Category:} Specific input fields for issue description and categorization.
        \item \textbf{Media Attachment:} Users can enrich their reports by attaching photos or videos.
        \item \textbf{Location Tagging:} Leverages GPS functionality for accurate location identification.
        \item \textbf{Issue Submission:} A clear call-to-action button for report submission.
        \item \textbf{Issue Subscription (Voting):} Encourages community involvement by allowing users to upvote issues reported by peers.
        \item \textbf{Issue Subscription (QR Code):} Enhances user engagement by letting them subscribe to issues via \gls{QR-code} scanning.
        \item \textbf{User Feedback on Resolved Issues:} Once an issue is resolved, a mechanism where users can provide feedback or rate the resolution can offer insights into the effectiveness of solutions.
    \end{itemize}

\subsection{Issue Tracking Interface}
    Dedicated to offering users a comprehensive overview of their reported issues, this interface encompasses:
    
    \begin{itemize}
        \item \textbf{Issue List Overview:} Displays a consolidated list of reported issues.
        \item \textbf{Issue Card Details:} Individual issue cards presenting a brief description, status, and timestamp.
        \item \textbf{Issue Details View:} Delving deeper, users can access more intricate details of an issue.
        \item \textbf{Filter and Search:} Facilitates easy navigation by providing filtering and searching capabilities.
        \item \textbf{Real-time Updates:} Keeps users abreast with real-time issue status changes.
    \end{itemize}

\subsection{User Account Management}
    A centralized hub for all user-centric operations, this interface includes:
    
    \begin{itemize}
        \item \textbf{Registration and Login:} Essential user registration and login functionalities.
        \item \textbf{Profile Settings:} A dedicated space for users to modify their profile settings.
        \item \textbf{Profile Customization:} Allows users to personalize their profiles.
        \item \textbf{Location Preferences:} Empowers users to set or modify their location preferences.
        \item \textbf{Log Out:} A clear option for users to securely log out from the application.
    \end{itemize}

\subsection{Dashboard Interface (Web-Based)}
    A strategic interface for local authorities and administrators, it encompasses:
    
    \begin{itemize}
        \item \textbf{Secure Login:} Ensures only authorized personnel gain access.
        \item \textbf{Overview Dashboard:} Offers a macroscopic view of all reported issues via an interactive map.
        \item \textbf{Issue List Management:} A comprehensive list of issues with advanced filtering options.
        \item \textbf{Issue Assignment and Monitoring:} Tools tailored for efficient issue assignment and progress monitoring.
        \item \textbf{Internal and External Communication:} Facilitates streamlined communication for internal messaging and user engagement.
        \item \textbf{Employee Management:} A managerial toolset for handling employee roles and responsibilities.
        \item \textbf{Workflow Customization:} Enables customization of the default issue resolution workflow.
    \end{itemize}

\subsection{Agent Interface}
    Crafted to equip agents with all necessary tools, this interface includes:
    
    \begin{itemize}
        \item \textbf{Issue Notifications:} Ensures agents are timely informed of new assignments.
        \item \textbf{Issue Status Updates:} Allows agents to update issue statuses on-the-go.
        \item \textbf{Notification Sign Generation:} Enables agents to disseminate public information via QR-code embedded signs.
        \item \textbf{Communication with Officers:} A channel for agents to liaise with officers.
        \item \textbf{Viewing Additional Comments:} Lets agents view and respond to user comments.
        \item \textbf{Issue Filtering:} Facilitates organization of issues based on their current status.
        \item \textbf{Workflow Visualization:} A \gls{Kanban board} showcasing the issue resolution process.
        \item \textbf{Request for Assignment:} Enables proactive assignment requests by agents.
    \end{itemize}

\subsection{Notification Interface}
    Tailored to keep users engaged, this interface ensures:
    
    \begin{itemize}
        \item \textbf{Push Notifications:} Direct notifications about issue updates and comments.
        \item \textbf{Quick Access:} Seamless transition from notifications to the relevant application section.
    \end{itemize}

