The \textbf{iBrief} application seamlessly integrates with a myriad of software interfaces and dependencies, ensuring a holistic and efficient user experience. The primary software interfaces encompass:

\begin{itemize}
    \item \textbf{Operating Systems:} The application is meticulously developed to ensure compatibility with both \gls{iOS} (Apple) and \gls{Android} (Google) mobile platforms.
    
    \item \textbf{Web Services and \gls{API}s:} Leveraging external web services and \gls{API}s, the application can fetch location data, dispatch push notifications, and perform secure data transactions.
    
    \item \textbf{Back-end System:} The \gls{back-end} infrastructure on \gls{AWS} orchestrates data processing, storage, and issue coordination, ensuring \gls{scalability} and robustness.
    
    \item \textbf{Database Management:} A sophisticated database management system is in place to meticulously handle user profiles, issue repositories, and other pivotal application data.
    
    \item \textbf{Third-Party Integration:} For enriched functionality, the application integrates with third-party systems, such as payment gateways for user rewards or analytical tools for performance metrics.
    
    \item \textbf{Security Protocols:} To ensure data integrity and user privacy, the application adopts advanced security protocols and encryption mechanisms.
\end{itemize}

Through these integrated software interfaces, the \textbf{iBrief} application promises a reliable, secure, and dynamic user interaction.

